Size, Shape and Functionality Dependence of Solute Transport Mechanisms in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-03-02 Ben_Manuscripts/transport/Outline.tex
Outline updates

%  There are a number of questions that we wish to answer in order to create a
%  framework for studying this system in even greater detail.
  There are a number of questions we wish to address in order to characterize
  transport in this system.
  \begin{enumerate}

   	\item What transport mechanisms do we observe?

@@

  	\item How do molecules, including water, partition within the pores?

@@

  	\item Can we describe the transport mechanisms using pre-existing 
  	mathematical models.

@@

  	\item How can we modify the current monomers in order to enhance
  	solute-specific separations?

@@

  There are number of questions this study is not intended to answer.
  \begin{itemize}
    \item We will not study the concentration dependence of the observed
    transport rates. Although the average MSD might change with concentration,
    we are focused on the underlying solute-membrane interactions that lead to
    the observed transport mechanisms which we conjecture will be the same 
    regardless of concentration.
    \item We will not study the chemical potential of solutes in the pores, which
    could give us a better understanding of equilibrium solute partitioning.
    However, this information will not greatly enhance our understanding of 
    mechanistic details in various membrane regions.
    \item Both of the above points will add unnecessary levels of complexity
    which can be left for a future study. 
%    \item Our work is meant as a simple starting point for studying transport
%    mechanisms in these complex LLC systems.
    \item This work is a simple starting point meant for observing the types
    of interactions which occur between isolated solutes and the membrane.
  \end{itemize}

@@

  We equilibrated an initial solvated configuration before adding solutes.
  \begin{itemize}
	\item We equilibrated the initial configuration using the `wet'
	equilibration procedure described in our previous work~\cite{coscia_understanding_2019}.
	\item We cross-linked the equilibrated solvated configuration using the
	cross-linking procedure described in our previous work. 
  \end{itemize}

  We added 6 solute molecules to each pore of the equilibrated cross-linked
  configuration.
  \begin{itemize}
	\item We equally spaced each solute in the pore
	\item 6 solutes per pore provided a balance of a useful amount of data
	for generating statistics and a low degree of interaction between solutes (reference
	to supporting information to show low degree of interaction)
	\item At each insertion point we placed a randomly oriented solute molecule
	then ran a short energy minimization.
	\item We allowed the solutes to equilibrate for 5 ns using berendsen 
	pressure control
	\item We collected transport data using 1 $\mu$s simulations
  \end{itemize}

%  \subsubsection*{Modeling subdiffusion}\label{method:model_sFBM}
%
%  Solutes in our H\textsubscript{II} LLC membrane exhibit subdiffusive
%  behavior, a type of anomalous diffusion. 
%  \begin{itemize}
%  	\item During an anomalous diffusion process, the mean squared displacement (MSD)
%  	does not grow linearly with time, rather it is of the form:
%	\begin{equation} 
%	\langle x^2(t) \rangle = K_{\alpha}t^\alpha
%	\label{eqn:msd_form}
%	\end{equation} 
%	where $\alpha$ is the anomalous exponent and $K_\alpha$ is the
%	generalized diffusion coefficient.
%	\item A value of $\alpha < 1$ indicates a subdiffusive process, while a value of
%	$\alpha = 1$ and $\alpha > 0$ is characteristic of Brownian and superdiffusive
%	motion respectively.
%  \end{itemize}
%
%  \noindent We calculated both the ensemble-averaged and time-averaged MSDs
%  of the simulated trajectories.
%  \begin{itemize}
%	\item The ensemble-averaged MSD measures the displacement of a particle from its initial
%	position~\cite{meroz_toolbox_2015} and can be written as
%	\begin{equation}
%	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle
%	\label{eqn:ensemble_msd}
%	\end{equation}
%%	\item The average MSD calculated in this way recovers the form of
%%	Equation~\ref{eqn:msd_form}. % time-averaged should recover it too for FBM 
%	\item The time-averaged MSD measures the displacement between all possible time lags
%	and can be written as
%	\begin{equation}
%	\overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
%	\end{equation}
%	where $\tau$ is the time lag and T is the length of the
%	trajectory~\cite{meroz_toolbox_2015}. 
%%	\item The time-averaged MSD becomes linear in our simulations,
%%	therefore we can fit a line to its slope in order to estimate the macroscopic
%%	diffusivity of the particle.
%	%BJC: this needs more justification. Not many people have done it
%	%BJC: could also not report them as diffusivities. Comparison of total MSD
%	% should give same information
%	% Linear region probably exists because dwell times on the order of large lag times
%	% become negligible
%  \end{itemize}
%  
%  \noindent Three common mathematical models for modeling anomalous subdiffusion processes include 
%  continuous time random walks (CTRW), fractional Brownian motion (FBM) and
%  random walks on fractals (RWF).\cite{meroz_toolbox_2015}
%  \begin{itemize}
%    \item FBM is common in crowded, viscoelastic environments where each step comes 
%    from a Gaussian distribution but is anti-correlated to its previous 
%    step.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
%    \item A CTRW is characterized by a distribution of hop lengths and 
%    dwell times, where each each step is characterized by independent random draws from 
%    each distribution.\cite{montroll_random_1965,morrin_three_2018}
%    \item An RWF is imposed by a system's geometry. Systems with tortuous pathways and dead
%    ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
%    \item The processes described above can happen alone or in combination.  	
%  \end{itemize}
%  
%  \noindent We believe that solutes in the system studied here exhibit subordinated 
%  fractional Brownian motion (sFBM) where the parent process is FBM and the 
%  leading process is a CTRW. 
%  \begin{itemize}
%  	\item The ensemble-averaged MSD differs from the time-averaged MSD, which
%  	is indicative of non-ergodicity, a trait inherent to CTRWs but not FBM or RWFs.~\cite{thiel_weak_2014}
%  	\item We also observe non-stationary $z$-coordinate traces of each solute's
%  	center of mass (COM). %BJC: figure of a z-coordinate trace in main text or in supporting info
%  	\item For a pure CTRW, the time-averaged MSD should be linear.
%  	~\cite{neusius_subdiffusion_2008,meroz_subdiffusion_2010}
%  	\item However, a typical time-averaged solute MSD is sublinear (see supporting
%  	information), which suggests that there is another underlying subdiffusive mechanism.
%  	\item The hop lengths recorded after each dwell period are anti-correlated (See supporting information)
%  	\item Given the viscoelastic nature of the monomers in our system, we believe
%  	the hop lengths can be modeled with FBM. 
% 	\item For subordinated FBM, it can be shown that
%  	\begin{equation}
%  	\langle x^2(t) \rangle \simeq t^{\alpha\beta}
%  	\end{equation}
%  	where $\alpha$ is the anomalous exponent characteristic of the leading CTRW process
%  	and $\beta$ is the anomalous exponent characteristic of the parent FBM process. 
%  \end{itemize}
%
%  \noindent We can characterize a CTRW process using the parameters which describe its
%  dwell time and hop length distribution.
%  \begin{itemize}
%	\item We used the \texttt{ruptures} python package in order to identify
%	breakpoints in solute trajectories.\cite{truong_ruptures:_2018} (See Supporting Information for more
%	details on chosen parameters. i.e. type of cost function, cost function penalty
%	tolerance, number of dimensions used)
%	\item The corresponding hop lengths and dwell times between break points were 
%	used to construct empirical distributions.
%	\item For solutes in our system, the distribution of hop lengths is
%	well-represented by a Gaussian distribution.~\cite{metzler_random_2000,
%	metzler_anomalous_2014,neusius_subdiffusion_2009}
%	\item We are most interested in the standard deviation, $\sigma$, of the 
%	hop length distribution.
%	\item The distribution of dwell	times is expected to fit a power law (or heavy-tailed)
%	distribution proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
%	\item Because we are limited to taking measurements at discrete values
%	dictated by the output frequency of our simulation trajectories, we fit the
%	empirical dwell times to a discrete power law distribution whose maximum
%	likelihood $\alpha$ parameter we calculated by maximizing the following
%	likelihood function: 
%        \begin{equation}
%	\mathcal{L}(\beta) = -n\text{ln}\zeta(\beta, x_{min}) -
%	\beta\sum_{i=1}^{n} \text{ln}~x_i 
%	\label{eqn:powerlaw_likelihood}
%	\end{equation}
%	where $\beta = 1 + \alpha$, $x_i$ are collected dwell time data points,
%	$n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
%	where $x_{min}$ is the smallest measured value of
%	$x_i$.~\cite{clauset_power-law_2009} 
%	\item We obtained distributions of the hop length standard deviations, $\sigma$, and
%	$\alpha$ using statistical bootstrapping.\cite{efron_introduction_1994} 
%  \end{itemize}
%  
%  \noindent FBM processes can be described using the Hurst parameter, $H$, where 
%  $H = \beta/2$.
%  \begin{itemize}
%  	\item Brownian motion is recovered for $H = 0.5$
%	\item The autocovariance function of hop lengths has the analytical form:~\cite{mandelbrot_fractional_1968}
%    \begin{equation}
%	\gamma(k) = \dfrac{1}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
%	\label{eqn:autocovariance}
%	\end{equation}
%	where $k$ is the number of increments between hops.
%	\item We obtained H by performing a least squares fit of Equation~\ref{eqn:autocovariance}
%	to the empirically measured autocovariance function.
%	\item We used statistical bootstrapping to generate a distribution of $H$ 
%	values. %BJC: can provide more detail in supporting or just reference python script
%  \end{itemize}
%
%%  We generated distributions of parameters for the dwell time and hop length
%%  distributions using statistical bootstrapping.
%%  \begin{itemize}
%%	\item For each type of distribution, we randomly selected $n$ data points from the empirical
%%	distribution with replacement.
%%	\item We repeated the fitting procedure described above for each of 200 bootstrap trials.
%%  \end{itemize} 
%
%%  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
%%  magnitude longer than our molecular simulations.
%  \noindent For each solute, we simulated 10000 sFBM trajectories for 1 $\mu$s each. 
%  \begin{itemize}
%	\item We constructed trajectories by simulating	sequences of dwell times and correlated 
%	hop	lengths generated based on parameters randomly chosen from our bootstrapped parameter
%	distributions.
%	\item We propagated each trajectory until the total time reached 1 $\mu$s, and truncated
%	the last data point so that the total time exactly equaled 1 $\mu$s. 
%    \item Valid comparisons are only possible between fixed length sFBM simulations. The
%    power law dwell time behavior gives rise to the aging phenomenon, embodied by
%    a decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
%    \item We reported the MSD after 1 $\mu$s with corresponding 95 \% intervals
%% Following probably better suited for supporting information, if included at all
%%	\item We randomly sample Gaussian hop lengths using the
%%	\texttt{numpy.random.normal} method of the \texttt{numpy} python package.
%%	\item We randomly sampled dwell times from a discrete power law
%%	distribution based on the recommendations of Clauset et
%%	al.~\cite{clauset_power-law_2009}: 
%%	\begin{equation}
%%	x = \lfloor
%%	(x_{min} - \tfrac{1}{2})(1 - r)^{-1/(\alpha - 1)} + \tfrac{1}{2} \rfloor
%%	\label{eqn:discrete_powerlaw_draws}
%%	\end{equation}
%%	where $r$ is randomly drawn from a uniform distribution which we simulated
%%	with \texttt{numpy.random.uniform}.
%%	\item We found that thermal noise does not significantly influence the MSD and
%%	therefore did not add any noise to the simulated trajectories. (See supporting info)
%  \end{itemize}
%
%%BJC: probably don't need to explain this in great detail
%%  \noindent We fixed the length of each simulated trajectory so that we could compare the total
%%  MSD between different solutes without the influence of the ageing phenomenon.
%%  \begin{itemize}
%%	\item Ageing is defined by the tendency of the average MSD to decrease
%%	as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
%%	\item The maximum measured dwell time can be no longer than the total length
%%	of a simulated trajectory. 
%%	\item As measurement time or trajectory length is increased, longer dwell times
%%	are incorporated into the calculation, lowering the average MSD. (See supporting
%%	info for demonstration)
%%	\item We can achieve consistent total MSDs with low uncertainty for
%%	simulated trajectories created with a given set of parameters if we fix the
%%	trajectory length (as opposed to total number of steps).  
%%  \end{itemize}

  \subsection*{Mean Squared Displacment}

  \subsection*{Radial Distribution Functions}

  We measured the average radial distance of each solute of interest from the pore
  centers.
  \begin{itemize}
	\item We binned the radial distances and then normalized by the volume
	of the annulus defined by the bin edges.
	\item Although the pores are often described as straight, they have a
	small degree of tortuosity which disrupts the RDF calcuation 
	\item We obtain the best RDF by constructing splines that run through the
	pore centers.
	\item We construct the splines by dividing the membrane into 20 slices
	in the $z$-direction. Within each slice, we calculate the location of 
	the pore centers based on the average location of the aromatic rings
	that make up the monomer head groups.
	\item When calculating the RDF, the radial distance from the pore center
	is based on the distance between the solute center-of-mass and the ($x$, $y$)
	coordinates of appropriate point on the spline.
  \end{itemize}

@@

  \subsection*{Governing Mechanisms}\label{section:mechanism_overview}

  We have gained a clearer picture of the general transport properties exhibited by
  this system through the collective study of all solutes. We will first answer the
  questions posed in the introduction in a general sense before addressing them with
  respect to specific molecules where exceptions occur.

  On the timescales simulated in our study, we observe subdiffusive behavior.  
  \begin{itemize}  
    \item Figure~\ref{fig:example_ztraces} plots the $z$-coordinate versus time of
  	3 representative ethanol centers of mass.
  	\item There are clear periods of entrapment separated by relatively large hops.
	\item The MSD calculated based on all ethanol molecules is plotted in Figure~\ref{fig:example_msd}
	and is sublinear.
	\item The long periods of entrapment likely lead to this sublinear, and thus
	subdiffusive, behavior.
  \end{itemize}

  \begin{figure}
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{colorful_example_ztraces.pdf}
  \caption{}\label{fig:example_ztraces}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{example_msd.pdf}
  \caption{}\label{fig:example_msd}
  \end{subfigure}
  \caption{}\label{fig:qualitative_mechanisms}
  \end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  Mathematical modeling 
  All solutes exhibit hop diffusion, characteristic of a continuous time random walk.	
  \begin{itemize}
  	\item The length of entrapment follows a power law distribution 
  	(Figure~\ref{fig:example_powerlaw}) and the distribution of hop lengths can be 
  	described with a Gaussian distribution (Figure~\ref{fig:example_hop_dist}).
  	\item Power law distributed dwell times are responsible for the ageing phenomenon
  	which causes the MSD curve to decrease with increasing measurement time as longer
  	dwell times get sampled.
  \end{itemize}

  \noindent The direction of each hop is anti-correlated to the direction of the previous hop.
  \begin{itemize}
  	\item Figure~\ref{fig:example_autocovariance} shows the autocovariance function of 
  	ethanol step vectors. % BJC: vectors because includes magnitude + direction. Better word?
  	\item The negative autocovariance at low values of k indicates anti-correlation
  	between steps. 
  	\item If solutes followed a pure CTRW mechanism, the autocovariance function would
  	decay to zero immediately.
  	\item Although the autocovariance function is relatively noise, due to the somewhat small
  	number of hops observed over the course of each solute trajectory, there is the least 
  	uncertainty at k=1, the most insightful data point. This behavior is consistent across
  	all solutes molecules. % Can put error bars on points
  	\item Therefore, we believe transport can be described as subordinated fractional Brownian
  	motion where the leading process is a CTRW with hops that are dictated by the parent
  	process, FBM.
  	\item Future publications will focus on modeling the solute's transport characteristics
  	with an sFBM model
  \end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% BJC: first iteration of figure after this before I decided to include a hop length and dwell time distribution
%  \begin{figure}
%  \centering
%  \includegraphics[width=\textwidth]{msd_ztrace_acf.pdf}
%  \caption{}\label{fig:msd_ztrace_acf}
%  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{example_msd.pdf}
  \caption{}\label{fig:example_msd}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{example_ztraces.pdf}
  \caption{}\label{fig:example_ztraces}
  \end{subfigure}
  \par\medskip
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{example_powerlaw.pdf}
  \caption{}\label{fig:example_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{example_hop_dist.pdf}
  \caption{}\label{fig:example_hop_dist}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{example_autocovariance.pdf}
  \caption{}\label{fig:example_autocovariance}
  \end{subfigure}
  \caption{All solutes show subdiffusive transport behavior inside the membrane's
  nanopores, similar to that exhibited by ethanol. (a) The time-averaged MSD of 
  ethanol is not linear which suggests transport is governed by an anomalous 
  subdiffusion process. (b) The $z$-coordinate trace of 3 representative ethanol
  COMs shows clear periods of entrapment separated by hops. (c) The distribution
  of dwell times follows a power law. (d) The distribution of hop lengths appears
  Gaussian. (e) Hops are anti-correlated to their previous hop as indicated by the
  negative value of the autocovariance function at $k$ = 1.}\label{fig:examples}
  \end{figure}

  % BJC: would it be better to report as a fraction of water MSD?
  % BJC: need MSDs of 5 wt % systems here too. Can narrow to study of 10 wt % systems after
  \noindent We calculated the time-averaged MSD of each solute in the set over the
  course of 1 $\mu$s MD simulations. 
  \begin{itemize}
    \item Because the MSDs are non-linear and because of the ageing phenomenon, we
    did not attempt to calculate a diffusion constant as one might for a Brownian
    particle with a linear MSD.
	\item Instead, the MSD values plotted in Figure~\ref{fig:all_msds} represent the
	average MSD of each solute after a 400 ns time lag.
  \end{itemize}

%  \subsubsection*{The Influence of Water Content on Macroscopic Diffusion Coefficients}
%
%  Solutes in systems with lower water content exhibit lower diffusion coefficients.
%  \begin{itemize}
%	\item Pores are more crowded when there is less water (show RDFs of each)
%	\item Not a linear function of pore size - radius increase by x, D increases by y
%	\item Larger influence on bigger molecules
%  \end{itemize}

  \begin{figure}
  \centering
  \includegraphics[width=\textwidth]{all_tamsds.pdf}  % include bar plot of MW to show it's non-monotonic
  \caption{}\label{fig:all_msds}
  \end{figure}

>>>>

%  There are a number of questions that we wish to answer in order to create a
%  framework for studying this system in even greater detail.
  \noindent There are a number of questions we wish to address in order to characterize
  transport in this system.
  \begin{enumerate}

   	\item What transport mechanisms do we observe? \label{question:mechanisms}

@@

  	\item How do molecules, including water, partition within the pores? \label{question:partition}

@@

  	\item Can we describe the transport mechanisms using pre-existing 
  	mathematical models. \label{question:math}

@@

  	\item How can we modify the current monomers in order to enhance
  	solute-specific separations? \label{question:math}

@@

  \noindent There are also a number of questions this study is not intended 
  to answer.
  \begin{itemize}
    \item We will not study the concentration dependence of the observed
    transport rates. Although the average MSD might change with concentration,
    we are focused on the underlying solute-membrane interactions that lead to
    the observed transport mechanisms which we conjecture will be the same 
    regardless of concentration.
    \item We will not study the chemical potential of solutes in the pores, which
    could give us a better understanding of equilibrium solute partitioning.
    This information will not greatly enhance our understanding of 
    mechanistic details in various membrane regions.
    \item Both of the above points will add unnecessary levels of complexity
    which can be left for a future study. 
%    \item Our work is meant as a simple starting point for studying transport
%    mechanisms in these complex LLC systems.
    \item This work is a simple starting point meant for observing the types
    of interactions which occur between isolated solutes and the membrane.
  \end{itemize}

@@

  \noindent We equilibrated an initial solvated configuration before adding solutes.
  \begin{itemize}
	\item We equilibrated the initial configuration using the `wet'
	equilibration procedure described in our previous work~\cite{coscia_understanding_2019}.
	\item We cross-linked the equilibrated solvated configuration using the
	cross-linking procedure described in our previous work. 
  \end{itemize}

  \noindent We added 6 solute molecules to each pore of the equilibrated cross-linked
  configuration.
  \begin{itemize}
	\item We equally spaced each solute in the pore
	\item 6 solutes per pore provided a balance of a useful amount of data
	for generating statistics and a low degree of interaction between solutes (reference
	to supporting information to show low degree of interaction)
	\item At each insertion point we placed a randomly oriented solute molecule
	then ran a short energy minimization.
	\item We allowed the solutes to equilibrate for 5 ns using berendsen 
	pressure control
	\item We collected transport data using 1 $\mu$s simulations
  \end{itemize}

  \subsection*{Mean Squared Displacement}\label{method:MSD}

  \noindent We measured the time-averaged mean squared displacement (MSD)
  of the centers of mass of each solute over the course of 1 $\mu$s MD 
  simulations using Equation~\ref{eqn:tamsd}.
  \begin{itemize}
    \item \begin{equation}
	\overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
	\label{eqn:tamsd}
	\end{equation}
	where $\tau$ is the time lag and T is the length of the
	trajectory~\cite{meroz_toolbox_2015}. 
	\item Generally, the MSD grows according to Equation~\ref{eqn:msd_form},
	\begin{equation} 
	\langle x^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
	\end{equation} 
	\item where $\alpha$ is the anomalous exponent and $K_\alpha$ is the
	generalized diffusion coefficient.
	\item A value of $\alpha < 1$ indicates a subdiffusive process, while a value of
	$\alpha = 1$ and $\alpha > 1$ is characteristic of Brownian and superdiffusive
	motion respectively.
	\item In practice, $\alpha$ corresponds to the growth of the \textit{ensemble}
	MSD given by Equation~\ref{eqn:ensemble_msd}~\cite{meroz_toolbox_2015}:
	\begin{equation}
	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle
	\label{eqn:ensemble_msd}
	\end{equation}
	\item The ensemble MSD is calculated with respect to a reference position and
	hence carries some dependence on its starting point.
	\item The time-averaged MSD averages over all possible time lags of a given 
	length, effectively eliminating any initial configuration dependence and generating
	an increased number of observations. 
	\item For ergodic systems, both types of MSDs will be equal.
	\item Since we have a small number of solutes with which to generate statistics
	and because we are not calculating values for $\alpha$ in this particular study,
	we will only use the time-averaged MSD.
  \end{itemize}

  %BJC: need to word this differently since I haven't talked about CTRW yet
  \noindent We fixed the length of each simulated trajectory so that we could compare
  the total MSD between different solutes without the influence of the ageing phenomenon.
  \begin{itemize}
	\item Ageing is defined by the tendency of the average MSD to decrease
	as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
	\item The maximum measured dwell time can be no longer than the total length
	of a simulated trajectory. 
	\item As measurement time or trajectory length is increased, longer dwell times
	are incorporated into the calculation, lowering the average MSD. (See supporting
	info for demonstration)
	\item Because the MSDs are non-linear and because of the ageing phenomenon, we
    did not attempt to calculate a diffusion constant as one might for a Brownian
    particle with a linear MSD.
	\item Instead, the reported values for MSD represent the average MSD for a given
	solute after a 400 ns time lag.
  \end{itemize}

%  \noindent Three common mathematical models for modeling anomalous subdiffusion processes include 
%  continuous time random walks (CTRW), fractional Brownian motion (FBM) and
%  random walks on fractals (RWF).\cite{meroz_toolbox_2015}
%  \begin{itemize}
%    \item FBM is common in crowded, viscoelastic environments where each step comes 
%    from a Gaussian distribution but is anti-correlated to its previous 
%    step.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
%    \item A CTRW is characterized by a distribution of hop lengths and 
%    dwell times, where each each step is characterized by independent random draws from 
%    each distribution.\cite{montroll_random_1965,morrin_three_2018}
%    \item An RWF is imposed by a system's geometry. Systems with tortuous pathways and dead
%    ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
%    \item The processes described above can happen alone or in combination.  	
%  \end{itemize}

%  \noindent We believe that solutes in the system studied here exhibit subordinated 
%  fractional Brownian motion (sFBM) where the parent process is FBM and the 
%  leading process is a CTRW. 
%  \begin{itemize}
%  	\item The ensemble-averaged MSD differs from the time-averaged MSD, which
%  	is indicative of non-ergodicity, a trait inherent to CTRWs but not FBM or RWFs.~\cite{thiel_weak_2014}
%  	\item We also observe non-stationary $z$-coordinate traces of each solute's
%  	center of mass (COM). %BJC: figure of a z-coordinate trace in main text or in supporting info
%  	\item For a pure CTRW, the time-averaged MSD should be linear.
%  	~\cite{neusius_subdiffusion_2008,meroz_subdiffusion_2010}
%  	\item However, a typical time-averaged solute MSD is sublinear (see supporting
%  	information), which suggests that there is another underlying subdiffusive mechanism.
%  	\item The hop lengths recorded after each dwell period are anti-correlated (See supporting information)
%  	\item Given the viscoelastic nature of the monomers in our system, we believe
%  	the hop lengths can be modeled with FBM. 
% 	\item For subordinated FBM, it can be shown that
%  	\begin{equation}
%  	\langle x^2(t) \rangle \simeq t^{\alpha\beta}
%  	\end{equation}
%  	where $\alpha$ is the anomalous exponent characteristic of the leading CTRW process
%  	and $\beta$ is the anomalous exponent characteristic of the parent FBM process. 
%  \end{itemize}

  \subsection*{Dwell and Hop Length Distributions}\label{method:hops_and_dwells}

  \noindent We measured the distribution of dwell times and hop lengths in order to test
  the hypothesis that solutes follow a CTRW process.
  \begin{itemize}
	\item We used the \texttt{ruptures} python package in order to identify
	breakpoints, times when hops occur, in solute trajectories.\cite{truong_ruptures:_2018}
	(See Supporting Information for more details on chosen parameters. i.e. type of cost 
	function, cost function penalty	tolerance, number of dimensions used)
	\item The corresponding hop lengths and dwell times between break points were 
	used to construct empirical distributions.
  \end{itemize}

  \subsection*{Radial Density Functions}

  We measured the average radial distance of each solute of interest from the pore
  centers.
  \begin{itemize}
	\item We binned the radial distances and then normalized by the volume
	of the annulus defined by the bin edges.
	\item Although the pores are often described as straight, they have a
	small degree of tortuosity which disrupts the RDF calcuation 
	\item We obtain the best RDF by constructing splines that run through the
	pore centers.
	\item We construct the splines by dividing the membrane into 10 slices
	in the $z$-direction. Within each slice, we calculate the location of 
	the pore centers based on the average location of the aromatic rings
	that make up the monomer head groups.
	\item When calculating the RDF, the radial distance from the pore center
	is based on the distance between the solute center-of-mass and the linearly
	interpolated ($x$, $y$)	coordinates of the pore center calculated based
	on the spline.
  \end{itemize}

  \subsection*{Identification of Hydrogen Bonds}

  Based on the geometric criteria proposed by Luzar and Chandler \cite{luzar_effect_1996},
  we determined a hydrogen bond to exist if the distance between the donor, D, and acceptor,
  A, atoms is less than 3.5 \AA~and the angle formed by D--H...A is less than 30\degree.
    %BJC: According to Luzar/Chandler: The range of a water molecule’s first coordination
    % shell is 3.5 Å, as determined from the oxygen-oxygen radial distribution function.
    % The amplitude of librations that break hydrogen bonds is ,~ 30 degrees, as estimated
    % from Debye-Waller factors
  \begin{itemize}
    \item Attempts to describe a hydrogen bond in the context of molecular simulations has
    yielded a number of definitions with no true consensus \cite{prada-gracia_quest_2013}.
	\item The geometry of hydrogen bonds has some dependence on the system being studied. 
    \item The definition of Luzar and Chandler is easily visualized for trajectories using
    the \texttt{hbonds} representation of the Visual Molecular Dynamics (VMD) software 
    package which allows us to directly check the validity of identified hydrogen bonds.
    %BJC: might need to update this if something better exists for nitrogen 
  \end{itemize}

@@

  \subsection*{Structure and Transport of Membrane Components}\label{section:membrane_components}

  %BJC: Probably do analysis on pure water system for this section.

  In contrast to our previous work with a solvent-free version of this membrane, the pore
  region of the 5 and 10 wt \% water systems are primarily filled with water and sodium
  ions.
  \begin{itemize}
    \item In dry systems, the pore center is densely filled with sodium ions and 
    head groups (See Ref~\cite{coscia_understanding_2019}).
    \item Figure~\ref{fig:component_densities} plots the densities of each
    membrane component.
    \item Water is densest at the center of each pore. 
    \item Sodium ions are densest within the pore region, which we define as the
    space between the pore center and the peak head group density.
    \item The peak density of sodium ions is not at the pore center in either case
    likely because they are still loosely associated with the monomer's 
    carboxylate head groups.
  \end{itemize}

  \noindent Pores in the 10 wt\% water system are wider and less crowded by monomers than
  those in the 5 wt\% water system.
  \begin{itemize}
    \item The peak head group density of 10 wt\% water systems is about 0.2 nm
    further from the pore center than the 5 wt\%
    \item The 5 wt \% water system has a non-negligible amount of tail group atoms
    that occupy the pore center.
  \end{itemize}

  %BJC: I'm not sure if would be better to normalize the densities so that the
  % shape of the sodium density is more pronounced
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_5wt.pdf}
  \caption{5 wt\% water}\label{fig:component_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_10wt.pdf}
  \caption{10 wt\% water}\label{fig:component_density_10wt}
  \end{subfigure}
  \caption{The radial densities of various monomer components paint a picture of the
  pore topology where the pore centers are primarily composed of water and sodium ions.
  The 5 wt \% system (a) appears to be much more crowded by monomers than the 
  10 wt \% system (b). Head groups in (a) are densest closer to the pore center than
  in (b). A small amount of tail components find their way close to the pore center 
  of the 5 wt \% system. }\label{fig:component_densities}
  \end{figure}

  The MSD of sodium and water become linear on long timescales.
  \begin{itemize}
    \item
  \end{itemize}

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{water_msd_comparison.pdf}
  \caption{Water}\label{fig:water_msd_comparison}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{na_msd_comparison.pdf}
  \caption{Sodium Ions}\label{fig:na_msd_comparison}
  \end{subfigure}
  \caption{}\label{fig:msd_comparison}
  \end{figure}

  Sodium coordinates with water.

  \noindent The diffusion constant of water is about 50 times faster than sodium.
  \begin{itemize}
    \item In a dilute sodium chloride solution, the diffusivity of sodium
    is about 4 times slower than water.
    \item The carboxylate groups, whose oxygen atoms each have a charge of -0.822
    keep the positively charged sodium ions relatively close and restricts their
    motion.
  \end{itemize}

  \subsection*{Mechanisms Governing Small Solute Transport}\label{section:mechanism_overview}

  \noindent The MSDs for the solutes studied in this work span a moderate range. 
  \begin{itemize}
    \item We plotted the 400 ns time-lag MSD for each solute in Figure~\ref{fig:all_msds}.
  	\item The fastest solute, methanol, has an MSD over 20 times greater than
  	the slowest, dimethyl formamide. 
  \end{itemize}

  \noindent The MSDs are not a monotonic function of solute size.
  \begin{itemize}
  	\item We plotted the solute size against their MSDs in Figure~\ref{fig:all_msds}.
  	\item Tetrose, our fifth largest solute, has an average MSD higher than more 
  	than half of all solutes studied. 
  	\item The two slowest solutes, DMF and THF, are smaller than 10 faster solutes.
  	\item Transport is clearly affected by factors other than molecular size. 
  \end{itemize}

  \begin{figure}
  \centering
  \begin{subfigure}{0.5\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}  % include bar plot of MW to show it's non-monotonic
  \caption{}\label{fig:all_msds}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
  \includegraphics[width=\textwidth]{msd_radius.pdf} 
  \caption{}\label{fig:msd_radius}
  \end{subfigure}
  \caption{}\label{fig:msds}
  \end{figure}

%  We have gained a clearer picture of the general transport properties exhibited by
%  this system through the collective study of all solutes. We will first address the
%  questions posed in the introduction in a general sense before addressing them with
%  respect to specific molecules, where exceptions occur.
%  \bigskip

  \noindent On the timescales simulated in our study, we observe subdiffusive behavior.
  %, providing the beginnings of an answer to question~\ref{question:mechanisms}.
  \begin{itemize}  
    \item Figure~\ref{fig:example_ztraces} plots the $z$-coordinate versus time of
  	3 representative ethanol centers of mass.
  	\item There are clear periods of entrapment separated by relatively large hops.
	\item The MSD calculated based on all ethanol molecules is plotted in Figure~\ref{fig:example_msd}
	and is sublinear.
	\item The long periods of entrapment likely lead to this sublinear, and thus
	subdiffusive, behavior.
  \end{itemize}

  Solutes partition out of the pore into the head group region and beyond which
  may lead to radially dependent transport mechanisms.
  \begin{itemize}
    \item It is clear from Figure~\ref{fig:example_ztraces} that the longest 
    periods of entrapment generally occur when solutes are far from the pore
    center.
    \item There is a high resistance to movement in the dense head group and
    tail regions.
    \item When hops occur, and where there is the most $z$-positional noise, 
    solutes are generally close to the pore center.
    %BJC: need a radial density of head groups, tails, water etc.
    \item Solutes can move relatively freely when they enter the pore region
    which is primarily composed of water molecules.
  \end{itemize}
